\sysfull

### 2017-08-08 paper/background.tex
reference correction and removed word ophran

As the figure illustrates, checkpoint-based systems risk violating the consistency of volatile and non-volatile memory~\cite{dino}. To maintain memory consistency, versioning systems~\cite{dino,ratchet} {\em version} a subset of non-volatile variables with the checkpointed execution context. Task-based systems~\cite{chain,alpaca}, which we focus on this work and discuss in detail next, ensure state is consistent by using programmer, compiler, and runtime support.

@@

There are several run time strategies to ensuring task idempotence. One approach, utilized by Alpaca~\cite{alpaca}, is to identify non-volatile data involved in WAR dependences in a task (like DINO~\cite{dino} and Ratchet~\cite{rachet} did for checkpoints), execute the task using buffered copies of those data, and commit the buffered copies before completing the task. Another strategy is to statically create multiple versions of non-volatile data shared by tasks and ensure by construction that no task reads and writes the same non-volatile memory location~\cite{chain}. Regardless of the idempotence strategy, the key to task-based execution is that fixed, statically defined tasks execute as though atomic, completing after zero or more attempts.

>>>>

As the figure illustrates, checkpoint-based systems risk violating the volatile and non-volatile memory consistency~\cite{dino}. To maintain consistency, versioning systems~\cite{dino,ratchet} {\em version} a subset of non-volatile variables with the checkpointed execution context. Task-based systems~\cite{chain,alpaca}, which we focus on this work and discuss in detail next, ensure state consistency by using programmer, compiler, and runtime support.

@@

There are several run time strategies to ensuring task idempotence. One approach, utilized by Alpaca~\cite{alpaca}, is to identify non-volatile data involved in WAR dependences in a task (like DINO~\cite{dino} and Ratchet~\cite{ratchet} did for checkpoints), execute the task using buffered copies of those data, and commit the buffered copies before completing the task. Another strategy is to statically create multiple versions of non-volatile data shared by tasks and ensure by construction that no task reads and writes the same non-volatile memory location~\cite{chain}. Regardless of the idempotence strategy, the key to task-based execution is that fixed, statically defined tasks execute as though atomic, completing after zero or more attempts.
